Constraining the High Density Nuclear Symmetry Energy with Pions

### 2019-08-14 MSU-thesis-estee.tex
Added Pion multiplicity document
Added more figures

% This is standard fontenc/inputenc for pdflatex
% If you use LuaLaTeX or XeLaTeX you should replace this with the fontspec package
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
%
% If the thesis office requires Times, we'll give them Times
% You can experiment with other font packages here if you like.
% If you are using XeLaTeX or LuaLaTeX load the Times or Times New Roman font with \setmainfont
\usepackage{newtxtext,newtxmath} 
%
% Load any extra packages here
%
% You must specify the title of your thesis, your name, the field of study (not department), and the year
\title{The syntax and semantics of phonology}
\author{Joe Linguist}
\fieldofstudy{Linguistics} % This should be in sentence case
\date{2017}

% If you want a dedication page, specify the text of the dedication here and uncomment the next command.
%
%\dedication{This thesis is dedicated to someone.}
%
\begin{document}

@@

\include{chapters/ch_nucleareos}
\include{chapters/ch_piontheory}
\include{chapters/ch_embed}
\include{chapters/ch_theorymodel}
\include{chapters/ch_tpc}
\include{chapters/ch_software}
\include{chapters/ch_experiment}
\include{chapters/ch_analysis}
\include{chapters/ch_results}

%
% If you have pages that must appear in landscape mode, use the [lscape] documentclass option
% and enclose the pages in a {landscape} environment.
%\clearpage\pagestyle{lscape} % first clear the page and change the pagestyle
%\begin{landscape}
%
% your landscape table(s) or figure(s) here
%
%\end{landscape}
%\pagestyle{plain} % remember to change the pagestyle back to plain
%
%
% If you have appendices, they would go here.  
% Comment these lines out if you don't
% If you have more than one appendix, you need to use 
%   \begin{appendices}
%   \chapter{First appendix}
%   \chapter{Second appendix}
%   \end{appendices}
%ch_nucleareos.txt~
\appendix
\chapter{Your appendix}
%
\backmatter
% The next lines add the dots back into the References/Bibliography heading
% of the TOC.  Only uncomment this if you need to put the dots back in having removed them for Chapter headings.
%
%\addtocontents{toc}{%
%   \protect\renewcommand{\protect\cftchapterdotsep} {\cftdotsep}}
%
\makebibliographypage % make the bibliography cover page
% Bibliography can be single spaced
%
\SingleSpacing
%
% Your bibliography command here (e.g. \bibliography{your-bib-file}) if using natbib
%
% Remember that although the bibliography is single spaced, there needs to
% be a blank line between entries. This is set by your bibliography package
% If you are using natbib it is \bibsep; if using biblatex it's \bibitemsep
\end{document}

>>>>

%IS THIS THE RIGHT BIB STYLE TO USE????!?!?!??!?!?!??!
%!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!
\bibliographystyle{elsarticle-num}

% This is standard fontenc/inputenc for pdflatex
% If you use LuaLaTeX or XeLaTeX you should replace this with the fontspec package
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{float}
\usepackage{graphicx}
\graphicspath{ {images/} }

%
% If the thesis office requires Times, we'll give them Times
% You can experiment with other font packages here if you like.
% If you are using XeLaTeX or LuaLaTeX load the Times or Times New Roman font with \setmainfont
\usepackage{newtxtext,newtxmath,booktabs,siunitx} 
%
% Load any extra packages here
%
% You must specify the title of your thesis, your name, the field of study (not department), and the year
\title{Constraining the High Density Nuclear Symmetry Energy with Pions}
\author{Justin Estee}
\fieldofstudy{Physics} % This should be in sentence case
\date{2019}

% If you want a dedication page, specify the text of the dedication here and uncomment the next command.
%
\dedication{This thesis is dedicated to someone.}
%

%User defined commands
\newcommand{\spirit}{S$\pi$RIT }
\newcommand{\ra}[1]{\renewcommand{\arraystretch}{#1}}
\includeonly{
%chapters/ch_intro,
%chapters/ch_theory,
chapters/ch_experiment,
chapters/ch_data_analysis,
%chapters/ch_data_analysis_2,
%chapters/ch_results
}

\begin{document}
%\sisetup{quotient-mode=fraction} % Output a/b as \frac{a}{b}

@@

\include{chapters/ch_intro}
\include{chapters/ch_theory}
\include{chapters/ch_experiment}
\include{chapters/ch_data_analysis}
\include{chapters/ch_data_analysis_2}
\include{chapters/ch_results}

%
% If you have pages that must appear in landscape mode, use the [lscape] documentclass option
% and enclose the pages in a {landscape} environment.
%\clearpage\pagestyle{lscape} % first clear the page and change the pagestyle
%\begin{landscape}
%
% your landscape table(s) or figure(s) here
%
%\end{landscape}
%\pagestyle{plain} % remember to change the pagestyle back to plain
%
%
% If you have appendices, they would go here.  
% Comment these lines out if you don't
% If you have more than one appendix, you need to use 
%   \begin{appendices}
%   \chapter{First appendix}
%   \chapter{Second appendix}
%   \end{appendices}
%ch_nucleareos.txt~
\appendix
\chapter{Your appendix}
%
\backmatter
% The next lines add the dots back into the References/Bibliography heading
% of the TOC.  Only uncomment this if you need to put the dots back in having removed them for Chapter headings.
%
%\addtocontents{toc}{%
%   \protect\renewcommand{\protect\cftchapterdotsep} {\cftdotsep}}
%
\makebibliographypage % make the bibliography cover page
% Bibliography can be single spaced
%
\SingleSpacing
%
% Your bibliography command here (e.g. \bibliography{your-bib-file}) if using natbib
%
% Remember that although the bibliography is single spaced, there needs to
% be a blank line between entries. This is set by your bibliography package
% If you are using natbib it is \bibsep; if using biblatex it's \bibitemsep
\bibliography{mybibfile}

\end{document}

### 2019-08-14 chapters/ch_data_analysis.tex
Added more figures

\chapter{Data Analysis I: Calibration and Corrections}
\section{Software}

@@

\section{Calibrations and Corrections}
Cocktail Calibration

\subsection{Electronics calibration}
Pulse the ground grid. 
Picture of calibration of channels before and after.

\subsection{Anode gain calibration}
Picture of low vs high gain channels and fit

@@

\subsection{Space Charge Corrections}
Overview
Discuss the relevant time scales, drift lengths, magnitudes, and locations of space charge
Figure of cartoon sheet charge
Figure of beam path locations for different beam types
Table of energy loss tables for energies and beam types
Reference appendix for poisson solver 
Tables for ion drift velocity in P-10 Gas reference Sauli
Figure of sDAC or POCA 
Figure of cartoon of what is happening to tracks
Figure of correction map in TPC and MC map 
Figure of before and after correction BDC vs reco momentum
Figure of track residuals before and after?

>>>>

\chapter{Data Analysis I: Calibration and Corrections}

Need to explain pedestal subtraction 
GG noise subtraction

\section{Software}

@@

\section{Calibrations and Corrections}

\subsection{Cocktail calibration}

\begin{table*}\centering
\ra{1.3}
\begin{tabular}{@{}rrrrcrrrcrrr@{}}\toprule
& \multicolumn{3}{c}{$100 MeV$} & \phantom{abc}& \multicolumn{3}{c}{$100 MeV$} &
\phantom{abc} & \multicolumn{3}{c}{$300 MeV$}\\
\cmidrule{2-4} \cmidrule{6-8} \cmidrule{10-12}
& &\multicolumn{2}{c}{Measured}\\
Particle &\phantom{abc} & Raw & E$\times$B\\
\midrule
p   & 882.8 & d & d & 903.5 & e & e &\phantom{abcdef} & f & f \\
d   & 817.1 & d & d & 898.5 & e & e & 1621.1 & f & f\\
t   & 589.5 & d & d & 887 & e & e & 1612.4 & f & f  \\
$^{3}$He  & 1617.3  & d & d & 1795.2 & e & e & 3236.4 & f & f\\
$^{4}$He  & 1405.6  & d & d & 1782.9 & e & e & 3226.4 & f & f \\
\bottomrule
\end{tabular}
\caption{Summary of expected cocktail. }
\label{tb:cocktailsummary}
\end{table*}

Cocktail Calibration 
Picture of cocktail before and after ExB effect
Table of LISE++ expected cocktail energies ridigity setting of dipole magnets (reference big rips line)

\subsection{Electronics calibration}
Pulse the ground grid. 
\begin{figure}[H]
\includegraphics[width=\linewidth]{gaincalib.png}
\caption{Calibration of electronics}
\label{fig:gaincalib}
\end{figure}

\subsection{Anode gain calibration}

\begin{figure}[H]
\includegraphics[width=\linewidth]{highlowcal.png}
\caption{Calibration of low high.}
\label{fig:highlowcal}
\end{figure}

Picture of low vs high gain channels and fit

@@

\subsection{Space Charge Corrections}
Overview
Discuss the relevant time scales, drift lengths, magnitudes, and locations of space charge

\begin{figure}[H]
\includegraphics[width=\linewidth]{spacechg_cartoon.png}
\caption{Location of space charge in 132 Sn}
\label{fig:spacechg_cartoon}
\end{figure}

\begin{figure}[H]
\includegraphics[width=\linewidth]{beampath.png}
\caption{Beam path of the experiments}
\label{fig:beampaths}
\end{figure}

Figure of beam path locations for different beam types
Table of energy loss tables for energies and beam types
Reference appendix for poisson solver 
Tables for ion drift velocity in P-10 Gas reference Sauli
Figure of sDAC or POCA 
Figure of cartoon of what is happening to tracks
Figure of correction map in TPC and MC map 
Figure of before and after correction BDC vs reco momentum
Figure of track residuals before and after?

### 2019-08-14 chapters/ch_experiment.tex
Added more figures

\begin{table*}\centering
\ra{1.3}
\begin{tabular}{@{}rr@{}}\toprule 
\multicolumn{2}{c}{\spirit TPC Overview} \\
 \midrule
Pad plane area & 1.3 m x .9 m\\
Pad size       & 1.2 cm x .8 cm \\
Number of pads & 12096 (112 x 108) \\
Gas composition& 90\% Ar + 10\% CH${}_4$  \\
Multiplicity limit & 200  \\
dE/dx range        & Z=1-8, $\pi$, p,d,t,He,Li-O \\
Drift length       & 50 cm \\
\bottomrule
\end{tabular}
\caption{Caption}
\end{table*}

\begin{table}
 \begin{tabular}{||c c c c||} 
 \hline
 \multicolumn{4}{|c|}{S$\pi$RIT TPC Overview} \\
 \hline
 Pad Plane Area & 1.3 m x 0.9 m & Gas Gain & 1000\\
 \hline
 Pad Size & 1.2 cm x 0.8 cm & Drift Velocity & 5.5 cm/$\mu$s \\
 \hline
 Number of pads & 12096 (112x108) & E-field & 135 V/cm  \\
 \hline
  Gas composition & 90\% Ar + 10\% CH${}_4$ & Multiplicity limit & 200  \\
 \hline
 Drift length & 50 cm & dE/dx range & Z=1-8, $\pi$, p,d,t,He,Li-O \\ [1ex] 
 \hline
\end{tabular}
\caption{An overview of the properties of the S$\pi$RIT TPC.}
\label{tb:spiritoverview}
\end{table}

@@

\begin{table}
 \begin{tabular}{||c c c c||} 
 \hline
 \multicolumn{4}{|c|}{GET Electronics Settings} \\
 \hline
 GET settings & All options & ${}^{132}$Sn + ${}^{124}$Sn & ${}^{124}$Sn + ${}^{112}$Sn \\
 \hline
 ADC bit range      & 14 bits &  &  \\
 \hline
 Sampling frequency & 1 - 100 MHz &   &    \\
 \hline
 Dynamic range      & .12,.24,1.0,10 pC & & \\
 \hline
 Peaking time       &  69,117,232,501,720, 1014 ns &  &   \\
 \hline
 Time bucket        & 512 & 270 & 270  \\
 \hline
\end{tabular}
\caption{Summary of the optional settings of the GET electronics and those used during the 20?????? experimental runs}
\label{tb:getoverview}
\end{table}

>>>>

\begin{table*}\centering
\ra{1.3}
\begin{tabular}{@{}rr@{}}\toprule 
\multicolumn{2}{c}{\spirit TPC Overview} \\
 \midrule
Pad plane area & 1.3 m x .9 m\\
Pad size       & 1.2 cm x .8 cm \\
Number of pads & 12096 (112 x 108) \\
Gas composition& 90\% Ar + 10\% CH${}_4$  \\
Multiplicity limit & 200  \\
dE/dx range        & Z=1-8, $\pi$, p,d,t,He,Li-O \\
Drift length       & 50 cm \\
\bottomrule
\end{tabular}
\caption{An overview of the properties of the \spirit TPC}
\label{tb:spiritoverview}
\end{table*}

@@

\begin{table*}\centering
\ra{1.3}
\begin{tabular}{@{}rr@{}}\toprule 
\multicolumn{2}{c}{GET electronics settings}\\
\midrule
ADC bit range       & 14 bits \\
Sampling frequency  & 1-100 MHz \\
Dynamic range       & .12, .24, 1.0, 10pC \\
Peaking time        & 69,117,232,501,720,1014 ns \\
Time bucket range   & 512\\
\bottomrule
\end{tabular}
\caption{Summary of range of GET electronics settings. }
\label{tb:getoverview}
\end{table*}
